### 2019-08-27 README.Rmd
updated to do list

- Paper
    - Can you re-explain your vision with the minipage format?
    - I cannot get LIME to work on my computer anymore...
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - show updated schedule
    - email list (should I be added as an admin?)
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
    - Are you still available to talk next week?

@@

- finish reading new paper
- add generalized R2 values to plots
- code up Laugel et al's work
- point out differences and similarities from the other paper (such as normal sampling)
- keep the LIME procedure at a higher level in the paper
- change to computing the $\mathcal{L}$ metric from the paper
- add figure descriptions in both caption and text
- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- read through papers giving an overview of the current explanation methods

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-other_explainers`: trying out other model explainers
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project

>>>>

- Paper
    - Can you re-explain your vision with the minipage format?
    - Sometimes LIME doesn't work on my computer anymore...
    - Explain the details of the locality paper to Heike (ask about the radius definition)
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - show updated schedule
    - email list (should I be added as an admin?)
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
    - Are you still available to talk next week?

@@

- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- point out differences and similarities from the other paper (such as normal sampling)
- code up Laugel et al's work
- read through papers giving an overview of the current explanation methods

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-literature_review`: notes on papers relating to LIME
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project
